\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning

### 2018-05-09 ccs/eval.tex
spell check

In Table~\ref{tab:nn}, 
the column ``Model size'' is the number of parameters in the
trained model.
We observe that our performance is competitive with specialized
\minion protocols, for both the LAN and the WAN settings. Further, lines
of \tool source code required is still small. 
We note that while the \minion implementation is based on the ABY framework, it does not use ABY ``off-the-shelf'' and performs application-specific optimizations. In contrast, \tool focuses on generic
\mpc and directly exploits the exisiting performant implementations in ABY.
% Optimizations such as those found in \minion are part of our future work.
\minion also reports performance results on a bigger DNN with 7
convolution layers. In \tool, this benchmark requires partitioning and
we discuss it in \sectionref{pipeeval}.

@@

\paragraph{Scalability.}  To
illustrate the scalability of partitioning, we evaluate a
sequence of DNNs with and without partitioning
(where every layer of each DNN is a separate stage) in~\figureref{partitioning}.
For DNNs with up to 4 (hidden) layers, the performance is almost idential and the lines overlap, thereby
illustrating that partitioning did not cause any noticeable performance overheads.
Memory issues start showing up in the non-partitioned implementation with the 5 layer DNN and it is slower.
Performance degrades rapidly thereafter and
DNNs with 6 or more layers fail to execute (terminate with a ``bus error").
However, the partitioned implementation scales well to even these large DNNs.

@@

We observe that in the LAN setting, we are about 19 times faster than~\cite{valeriaMatrix} and in the WAN
setting we are about 4 times faster. The main source of these significant speedups is that, unlike~\cite{valeriaMatrix}, \tool does not need to convert the functionality into boolean circuits. 
However, this benchmark requires more lines of code than the previous benchmarks
because of  Batcher's sort (450 lines of \tool code in each stage).
However, the current programmer effort seems miniscule compared to the mammoth implementation effort
put in by Nikolaenko et al. (Section 5 of ~\cite{valeriaMatrix}) to scale a boolean circuits based
backend to this benchmark.

>>>>

In Table~\ref{tab:nn}, 
the column ``Model size'' is the number of parameters in the
trained model.
We observe that our performance is competitive with specialized
\minion protocols, for both the LAN and the WAN settings. Further, lines
of \tool source code required is still small. 
We note that while the \minion implementation is based on the ABY framework, it does not use ABY ``off-the-shelf'' and performs application-specific optimizations. In contrast, \tool focuses on generic
\mpc and directly exploits the existing performant implementations in ABY.
% Optimizations such as those found in \minion are part of our future work.
\minion also reports performance results on a bigger DNN with 7
convolution layers. In \tool, this benchmark requires partitioning and
we discuss it in \sectionref{pipeeval}.

@@

\paragraph{Scalability.}  To
illustrate the scalability of partitioning, we evaluate a
sequence of DNNs with and without partitioning
(where every layer of each DNN is a separate stage) in~\figureref{partitioning}.
For DNNs with up to 4 (hidden) layers, the performance is almost identical and the lines overlap, thereby
illustrating that partitioning did not cause any noticeable performance overheads.
Memory issues start showing up in the non-partitioned implementation with the 5 layer DNN and it is slower.
Performance degrades rapidly thereafter and
DNNs with 6 or more layers fail to execute (terminate with a ``bus error").
However, the partitioned implementation scales well to even these large DNNs.

@@

We observe that in the LAN setting, we are about 19 times faster than~\cite{valeriaMatrix} and in the WAN
setting we are about 4 times faster. The main source of these significant speedups is that, unlike~\cite{valeriaMatrix}, \tool does not need to convert the functionality into boolean circuits. 
However, this benchmark requires more lines of code than the previous benchmarks
because of  Batcher's sort (450 lines of \tool code in each stage).
However, the current programmer effort seems minuscule compared to the mammoth implementation effort
put in by Nikolaenko et al. (Section 5 of ~\cite{valeriaMatrix}) to scale a boolean circuits based
backend to this benchmark.

### 2018-05-09 ccs/ex.tex
spell check

\subsection{Comparison with Yao-only approach}
\label{sec:oblivm}
We show that it is critical to use a mix of arithmetic and boolean circuits  for performance.
 Previous work has observed that Yao's garbled circuits do not scale to machine learning examples that require a large number of multiplications~\cite{aby,tasty,autoS,secureml,minionn,chameleon}.
Indeed, this is one of the main drivers behind the development of various specialized MPC protocols in previous works~\cite{secureml,minionn,shafindss} (we compare against them in~\sectionref{eval}) .
Here, we empirically demonstrate the performance benefits of mixed computations over boolean-only compute by comparing with state of the art Yao-based compilers CBMC-GC~\cite{cbmcgc} and ObliVM~\cite{oblivm}.

@@

 Converting
an arithmetic share to a boolean share requires computing a garbled
circuit for addition. The size of this circuit grows  linearly in the bitwidth of the inputs. Similarly, converting from boolean to arithmetic requires computing a 
garbled circuit for subtraction, which is also linear. 
Since each conversion has roughly the same cost as a boolean addition,
 \tool performs
addition using a boolean circuit
if the operands  are boolean shared, else it uses an arithmetic
circuit.

For multiplication, \tool always chooses
an arithmetic circuit, as the cost of a boolean multiplication is much
higher than the cost of converting the operands from boolean to
arithmetic, performing an arithmetic multiplication, and then converting
the result back to boolean ($\sim9x$ more time $\&$ $\sim20x$ more
communication in a LAN setting). Theoretically, the size of a boolean multiplication circuit is quadratic in the bitwidth, which causes this performance gap.
Roughly, multiplying two $64$-bit integers using arithmetic sharing requires only $2$ multiplications, whereas Yao requires at least $4096$ AES operations in the online phase.
Since this gap is quite large, we believe that this choice is optimal for realistic network
settings. Finally, \tool chooses boolean circuits for all
the operations lacking arithmetic support in ABY, e.g., comparisons, bit-shifts, etc.

>>>>

\subsection{Comparison with garbled circuits}
\label{sec:oblivm}
We show that it is critical to use a mix of arithmetic and boolean circuits  for performance.
 Previous work has observed that Yao's garbled circuits do not scale to machine learning examples that require a large number of multiplications~\cite{aby,tasty,autoS,secureml,minionn,chameleon}.
Indeed, this is one of the main drivers behind the development of various specialized \mpc protocols in previous works~\cite{secureml,minionn,shafindss} (we compare against them in~\sectionref{eval}) .
Here, we empirically demonstrate the performance benefits of mixed computations over boolean-only compute by comparing with state of the art Yao-based compilers CBMC-GC~\cite{cbmcgc} and ObliVM~\cite{oblivm}.

@@

 Converting
an arithmetic share to a boolean share requires computing a garbled
circuit for addition. The size of this circuit grows  linearly in the bit-width of the inputs. Similarly, converting from boolean to arithmetic requires computing a 
garbled circuit for subtraction, which is also linear. 
Since each conversion has roughly the same cost as a boolean addition,
 \tool performs
addition using a boolean circuit
if the operands  are boolean shared, else it uses an arithmetic
circuit.

For multiplication, \tool always chooses
an arithmetic circuit, as the cost of a boolean multiplication is much
higher than the cost of converting the operands from boolean to
arithmetic, performing an arithmetic multiplication, and then converting
the result back to boolean ($\sim9x$ more time $\&$ $\sim20x$ more
communication in a LAN setting). Theoretically, the size of a boolean multiplication circuit is quadratic in the bit-width, which causes this performance gap.
Roughly, multiplying two $64$-bit integers using arithmetic sharing requires only $2$ multiplications, whereas Yao requires at least $4096$ AES operations in the online phase.
Since this gap is quite large, we believe that this choice is optimal for realistic network
settings. Finally, \tool chooses boolean circuits for all
the operations lacking arithmetic support in ABY, e.g., comparisons, bit-shifts, etc.

### 2018-05-09 ccs/main.tex
minor
spell check

\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Anonymous submission \#9999 to ACM CCS 2017} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

@@

\title{\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation \dg{for Machine Learning}}

>>>>

\fancyhf{} % Remove fancy page headers 
\fancyhead[C]{Anonymous submission \#410 to ACM CCS 2017} % TODO: replace 9999 with your paper number
\fancyfoot[C]{\thepage}

@@

\title{\tool: Programmable, Efficient, and Scalable \\ Secure Two-Party Computation for Machine Learning}

### 2018-05-09 ccs/security.tex
spell check

%\vspace{-0.2in}
\paragraph{Security theorem.} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01} and provide provable security against all side-channel attacks.
At a very high level, in this
framework, parties are modeled as non-uniform interactive turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with $\env$ that observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit based on the output of the honest party and the view of the adversary. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the  distribution ensemble
describing $\env$'s output in this interaction. 
In the ideal interaction, parties send their inputs to  a
trusted functionality that performs the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this ideal execution, and $\ideal_{\F,\simu,\env}$
the distribution ensemble describing $\env$'s output after
interacting with the ideal adversary $\simu$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, the above two
distribution ensembles  are computationally indistinguishable.

>>>>

%\vspace{-0.2in}
\paragraph{Security theorem.} The protocols we generate provide
simulation-based security against a semi-honest adversary, in the
framework of ~\cite{gmw,can00,can01} and provide provable security against all side-channel attacks.
At a very high level, in this
framework, parties are modeled as non-uniform interactive Turing
machines (ITMs), with inputs provided by an environment $\env$. An
adversary $\adv$, selects and ``corrupts'' one of the parties -
however, $\adv$ still follows the protocol specification. $\adv$
interacts with $\env$ that observes the view of the corrupted
party. At the end of the interaction, $\env$ outputs a single bit based on the output of the honest party and the view of the adversary. Two
different interactions are defined: the {\em real world} and an {\em
  ideal world}. In the real interaction, the parties run the protocol
$\prot$ in the presence of $\adv$ and $\env$. Let
$\real_{\prot,\adv,\env}$ denote the  distribution ensemble
describing $\env$'s output in this interaction. 
In the ideal interaction, parties send their inputs to  a
trusted functionality that performs the desired
computation truthfully. Let $\simu$ (the simulator) denote the
adversary in this ideal execution, and $\ideal_{\F,\simu,\env}$
the distribution ensemble describing $\env$'s output after
interacting with the ideal adversary $\simu$. A
protocol $\prot$ is said to {\em securely realize} a functionality
$\F$ if for every adversary $\adv$ in the real interaction, there is
an adversary $\simu$ in the ideal interaction, such that no
environment $\env$, on any input, can tell the real interaction apart
from the ideal interaction, except with negligible probability (in the
security parameter $\secparam$). More precisely, the above two
distribution ensembles  are computationally indistinguishable.
